\chapter{Conclusion and Recommendation}
\label{chapter:conclusion}

\section{Conclusion}




\section{Recommendations}
Several recommendations for future work can be made. 

First, the Node Method should be replaced with an implicit 
approach to solving the pipeline temperature dynamics. As discussed, the 
explicit nature of the Node Method forces the small timestep of 1 second 
through the CFL condition. An implicit method allows considerably larger timesteps. This would reduce the simulation time and relax the pressure that the small timestep places on the steady-state assumptions of the heat exchanger and valve models.

Second, several component models could be made more realistic. The pump is 
currently restricted to a single head curve, and a more sophisticated model incorporating variable shaft speeds would better capture its behavior. Likewise, a more detailed model of the ATES and of the heat supply would improve the model's realism. Extending the network with additional components, such as multiple producers or storage 
buffers, would further broaden the range of systems the model can represent.

Third, more realistic heat demand profiles. Incorporating measured demand data would increase the fidelity of the simulations and, in turn, the relevance of the optimization results.

Fourth, the simulation should be run over a longer period in combination with a longer warm-up time. As noted in the discussion, the 6-hour warm-up is based on the stabilization of the bypass valve sensor temperature and does not guarantee that the water and pipe temperatures have reached steady state. A longer horizon would reduce the influence of the initialization settings on the results.

Finally, the cost function could be expanded to better reflect the operational priorities of the network. Combined with a sensitivity analysis of the optimization under noisy observations, this would provide a more complete and realistic basis for evaluating the control policy.





% - applying another method than the Node method which is uses an implicit approach in order to get rid of the small timesteps. 
% - And addin gmore realistic model of the ATES and pump and expanding with other compnents would be interesting
% -more realistic model of the heat demand
% - perform the simulation with over a longer amount of time in combination with a longer warm up time to lower the effect of the initialization settings
% - expand the cost function


% - making use of an average heat demand profile
\todo[inline]{specify added value of thesis}