\chapter{Physical constants}\label{chap::constants}

\section{Pipes}
These are the physical constants used for the pipes, shown for DN20, DN25, DN32, DN40 and the used values to validate the thermodynamic pipeline model of Van der Heijde et al \cite{VANDERHEIJDE2017158}. 

\begin{table}[h!]
\centering
\caption{Common pipe parameters for all DN pipe configurations and the van der Heijden experiment.}
\label{tab:pipe_dn_common}
\begin{tabular}{llll}
\hline
\textbf{Parameter} & \textbf{Symbol} & \textbf{Unit} & \textbf{Value} \\
\hline
Pipe density            & $\rho_{pipe}$   & kg/m$^3$          & 8000                 \\
Insulation density      & $\rho_{insu}$   & kg/m$^3$          & 32                   \\
Pipe heat capacity      & $c_{p,pipe}$    & J/(kgK)           & 500                  \\
% Insulation heat capacity& $c_{p,insu}$    & J/(kgK)           & 2500                 \\
Pipe conductivity       & $k_{pipe}$      & W/(mK)            & 14.9                 \\
Insulation conductivity & $k_{insu}$      & W/(mK)            & 0.04                 \\
Convection coefficient  & $\bar{h}$       & W/(m$^2$K)        & 5                    \\
Pipe roughness          & $\epsilon$      & m                 & $4.5 \times 10^{-5}$ \\
\hline
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{Geometry parameters for DN20, DN25, DN32 and DN40 \cite{VIB2025}.}
\label{tab:pipe_dn_geometry}
\begin{tabular}{lllllll}
\hline
\textbf{Parameter} & \textbf{Symbol} & \textbf{Unit} & \textbf{DN20} & \textbf{DN25} & \textbf{DN32} & \textbf{DN40} \\
\hline
Inner radius         & $r_a$  & m & 0.0100 & 0.0125 & 0.0160 & 0.0200 \\
Outer radius         & $r_b$  & m & 0.0135 & 0.0169 & 0.0210 & 0.0242 \\
Insulation thickness & $d_{\text{insu}}$     & m & 0.021  & 0.025  & 0.029  & 0.031  \\
\hline
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{Geometry parameters for the van der Heijden experiment configuration.}
\label{tab:pipe_heijden_geometry}
\begin{tabular}{llll}
\hline
\textbf{Parameter} & \textbf{Symbol} & \textbf{Unit} & \textbf{Value} \\
\hline
Inner radius         & $r_a$  & m & 0.02624 \\
Outer radius         & $r_b$  & m & 0.02819 \\
Insulation thickness & $d_{\text{insu}}$     & m & 0.013   \\
\hline
\end{tabular}
\end{table}

\section{Thermostatic bypass valve}


\section{Heat exchangers}
The thermal conductance at design point and the pressure loss coefficient are 
deducted from the information brochure of the Arctic WKW-S 4P 
\cite{fortes_wkw_s_4p}. The PI-controller values were chosen after some tuning, resulting in a controller that is neither saturated nor closing unrealistically rapid. The hydraulic conductivity required considerably more work, as no accurate value was provided in the brochure.

To determine a realistic $K_{vs}$, the valve positions required to reproduce a 
measured mass flow distribution in the network are first derived, after which the range of $K_{vs}$ values that maps these positions onto physically valid valve lifts $h \in [0, 1]$ is established. The mass flow distribution is obtained from fluid velocity data generated by an in-house steady-state model used by Eneco for a 23-floor building, provided by Rutger, from which the mass flows per pipe segment are computed directly.

The loop residual is evaluated at these mass flows, with the valve contribution separated from the remaining friction and pump terms. Following the pressure loss definitions from Section~\ref{sec::hydromodel}, the pressure loss vector without valve contributions is:

\begin{equation}
    \mathbf{f} = f \frac{8L}{\pi^2 D^5 \rho_w} + K_p
\end{equation}

\noindent giving the loop residual:

\begin{equation}
    \mathbf{r}_{\text{loop}} = \mathbf{L}\,\Delta p_{\text{pump}} - 
    \mathbf{L}\left(\mathbf{f} \cdot |\dot{\mathbf{m}}| \cdot \dot{\mathbf{m}}\right)
\end{equation}

\noindent where $\mathbf{L}$ is the loop matrix and $\Delta p_{\text{pump}}$ is the pump pressure evaluated at the known mass flows following \ref{eq::pump2order}. This residual must be absorbed by the valve pressure drops. Following \ref{eq::valvedp}, the valve contribution to the loop equations is:

\begin{equation}
    \mathbf{r}_{\text{valve}} = \mathbf{L}\left(\boldsymbol{\delta}_v \cdot 
    |\dot{\mathbf{m}}| \cdot \dot{\mathbf{m}}\right)
\end{equation}

\noindent where $\boldsymbol{\delta}_v$ is a binary vector indicating which pipes 
contain a valve. Since $\Delta p_v = \dot{m}|\dot{m}| / K_v^2$ from 
(\ref{eq::valvedp}), requiring loop closure yields:

\begin{equation}
    K_v = \sqrt{\frac{\mathbf{r}_{\text{valve}}}{\mathbf{r}_{\text{loop}}}}
    \label{eq:Kv_fit}
\end{equation}

\noindent These $K_v$ values are verified with the Newton-Raphson solver, 
recovering the original mass flow distribution with a residual of order 
$\mathcal{O}(10^{-8})$ kg/s. The valid $K_{vs}$ range is then determined in the following section.

\todo[inline]{need to still add the part of how to determine Kvs also further elaborate with the dimsnesions of the arrays}

\begin{table}[h!]
\centering
\caption{Heat exchanger and valve parameters.}
\label{tab:hex_constants}
\begin{tabular}{llll}
\hline
\textbf{Parameter} & \textbf{Symbol} & \textbf{Unit} & \textbf{Value} \\
\hline
Thermal conductance at design point  & $UA_{\text{des}}$            & W/K        & 2625    \\
Pressure loss coefficient          & $K_{p,dp}$     & 1/(kg m)          & 160     \\
Hydraulic conductivity & $K_{vs}$       & kg/(s Pa$^{0.5}$) & 0.003   \\
Proportional gain                  & $K_p$          & --                & 0.02    \\
Integral gain                      & $K_i$          & --                & $1\times10^{-5}$ \\

\hline
\end{tabular}
\end{table}


\section{Pumps}